Processing of visual and non-visual naturalistic spatial information in the "parahippocampal place area"

### 2021-02-24 paper/main.tex
try to make "Hemodynamic Modeling" (2.7) easier to understand

\todo[inline]{I think you need to help the reader understand, what annotations
in the AV-movie are relevant in the current context; COH: imo that is more
important in context of the contrasts (-> check if it is sufficiently described
there); might fit in here, too, but makes current part unnessecarily
complicated}

@@

    \caption{Overview of annotated stimulus features of the audio-visual

@@

@@

\todo[inline]{add a summary to the end of section 2.7 explaining in 2 sentences,
what regressors you will be focussing on -> easier for those that got confused
on the way}
% AV design matrix
The design matrices of the first-level time-series GLM analysis comprised the
regressors for the stimulus features listed in Tables~\ref{tab:events} and
\ref{tab:events} for the movie and audio-description stimulus, respectively.
% AD regressors in AV
Additionally, the design for the movie stimulus also contained the
regressors based on nouns used by the audio-description's narrator to indicate
a switch to another setting (categories \texttt{se\_new} and \texttt{se\_old}),
in order to be able to implement cross-modal control contrasts.
% AV regressors in AV
Likewise, the audio-description design matrix included movie cut related regressors
listed Table~\ref{tab:events} (excluding \texttt{no\_cut}).
% both stimuli: null regressors
For both stimuli, a null regressor was used for any event category in a segment
for which no event of a category was present (e.g. no event of
\texttt{vpe\_old} in segment 3; Tab.~\ref{tab:events}).
% temporal derivatives
Temporal derivatives of all regressors were added to the design matrix to compensate for
regional differences \citep{friston1998event}.
% motion parameters
Lastly, six participant and run specific motion estimated (translation and rotation)
were also included.
% high-pass filtering
The design matrices were temporally filtered with the same high-pass filter (cutoff period of
\unit[150]{s}) as the BOLD time series.

@@

@@

\todo[inline]{"vse, vno, vpe,..." are not really the most intuitive regressor
names -> ausschreiben, wo möglich}
% AV: primary contrast
In the primary contrast for the movie stimulus, we contrasted cuts to a setting
that was not depicted before (\texttt{vse\_new}) to cuts merely switching the
camera position within a setting that was already established earlier in the
movie (\texttt{vpe\_old}), because the former are designed to orient the viewer
in the movie environment using wider-camera angles, whereas the latter can
afford to depict details of a scene.
% AD: primary contrast
In the primary contrast of the audio-description stimulus, we contrasted
mentions of buildings and landmarks (\texttt{geo}), and rooms and
geometry-defining objects (\texttt{groom}) with nouns referring to a person's
head or face (\texttt{fahead}), and other non-geometry related categories
(\texttt{body}, \texttt{bodypart}, \texttt{fahead}, \texttt{object},
\texttt{sex\_f}, \texttt{sex\_m}).

>>>>

\todo[inline]{I think you need to help the reader understand, what annotations
in the AV-movie are relevant in the current context; COH: imo that is more
important in context of the contrasts; in any case: "cinematographic rationale" is now mentioned first,
then the categories are listed}

@@

    \caption{Overview of event categories of the audio-visual

@@

    Event categories of the movie are based on an annotation of cuts and
    depicted locations.
    Event categories of the audio-description based on an annotation of speech.

@@

\todo[inline]{add a summary to the end of section 2.7 explaining in 2 sentences,
what regressors you will be focussing on -> easier for those that got confused
on the way}
% AV design matrix
The design matrix for the first-level time-series GLM analysis of the movie
comprised regressors for the 12 event categories of the movie listed in
Table~\ref{tab:events}.
% AD design matrix
Similarly, the design matrix for the analysis of the audio-description comprised
regressors for the 13 event categories of the audio-description, also listed in
Table~\ref{tab:events}.
% AD regressors in AV
In order to implement cross-modal control contrasts, the design matrix for the
movie stimulus also contained the regressors based on nouns used by the
audio-description's narrator to indicate a switch to another setting (categories
\texttt{se\_new} and \texttt{se\_old}).
% AV regressors in AV
Likewise, the design matrix for the audio-description included the five movie
cut related regressors (\texttt{vse\_new}, \texttt{vse\_old}, \texttt{vlo\_ch},
\texttt{vp\_new}, \texttt{vpe\_old}).
% both stimuli: null regressors
For both stimuli, a null regressor was used for any event category in a segment
for which no event of a category was present (e.g. no event of \texttt{vpe\_old}
in segment 3; Tab.~\ref{tab:events}).
% temporal derivatives
Temporal derivatives of all regressors were added to the design matrix to
compensate for regional differences \citep{friston1998event}.
% motion parameters
Lastly, six participant and run specific motion estimated (translation and
rotation) were also included.
% high-pass filtering
The design matrices were temporally filtered with the same high-pass filter
(cutoff period of \unit[150]{s}) as the BOLD time series.

@@

\todo[inline]{SE: "vse, vno, vpe,..." are not really the most intuitive regressor names -> ausschreiben, wo möglich}

@@

% AV: primary contrast
In the primary contrast for the movie stimulus, we contrasted cuts to a setting
that was not depicted before (\texttt{vse\_new}) to cuts merely switching the
camera position within a setting that was already established earlier in the
movie (\texttt{vpe\_old}), because the former are designed to orient the viewer
in the movie environment using wider-camera angles, whereas the latter can
afford to depict details of a scene.
% AD: primary contrast
In the primary contrast of the audio-description stimulus, we contrasted
mentions of buildings and landmarks (\texttt{geo}), and rooms and
geometry-defining objects (\texttt{groom}) with nouns referring to a person's
head or face (\texttt{fahead}), and other non-geometry related categories
(\texttt{body}, \texttt{bodypart}, \texttt{fahead}, \texttt{object},
\texttt{sex\_f}, \texttt{sex\_m}).
